DALEX_TechQualityControl

### 2021-02-24 DALEX.Rmd
more plots for DALEx and default preferences updates for app.R

# final cleanup and factoring  
aoc_z$Species <- as.factor(paste(aoc_z$genus,aoc_z$species)) #must make value 'Species" (uppercase)
aoc_z$Group <- as.factor(aoc_z$organism.group) #must make value "Group"
aoc_z$Group <- fct_explicit_na(aoc_z$Group) #makes sure that species get counted even if they're missing a group
```
## Data Selection
```{r}
df <- aoc_z %>% 
  filter(tech.tier.zero == "N") %>% #gives studies that pass technical quality criteria
  dplyr::select(c(organism.group, exposure.duration.d, lvl1_f, dose.um3.mL.master, dose.mg.L.master, dose.particles.mL.master, life.stage, bio.org, polymer, shape, size.length.um.used.for.conversions, treatments, effect, effect.metric, particle.volume.um3, density.mg.um.3, environment, exposure.route, lvl2_f)) %>% 
  mutate(effect.metric = as.character(effect.metric)) %>% 
  mutate(effect.metric = (case_when(
    effect.metric == "NONEC" ~ "NOEC",
    effect.metric == "HONEC" ~ "NOEC",
    effect.metric == "LOEC" ~ "LOEC",
    effect.metric == "LC50" ~ "LC50",
    effect.metric == "EC50" ~"EC50",
    effect.metric == "EC10" ~ "EC10"
  ))) %>% 
  mutate(effect.metric = replace_na(effect.metric,"not_available")) %>% 
  mutate(effect.metric = as.factor(effect.metric)) %>% 
  drop_na() %>%  #drop missing
mutate_if(~is.numeric(.) && (.) > 0, log10) %>% 
  mutate(effect_10 = case_when( #convert ordinal to numeric
      effect == "Y" ~ 1,
      effect == "N" ~ 0
    )) %>%
  mutate(effect_10 = factor(effect_10)) %>% 
  dplyr::select(-(effect))

@@

#classif_logicBag <- train(effect_10~., data = train, method = "logicBag", ntree = 100)

@@

explainer_classif_xgbTree <- DALEX::explain(classif_svm,  label = "eXtreme Gradient Boosting Trees", 
                                        data = test, y = yTest)

#explainer_classif_logicBag <- DALEX::explain(classif_svm,  label = "Bagged Logic Regression", 
                                       # data = test, y = yTest)

```
# Modelling
## Model Performance
```{r model performance, include=FALSE}
mp_classif_rf <- model_performance(explainer_classif_rf)
mp_classif_glm <- model_performance(explainer_classif_glm)
mp_classif_svm <- model_performance(explainer_classif_svm)
mp_classif_decTree <- model_performance(explainer_classif_decTree)
mp_classif_nnet <- model_performance(explainer_classif_nnet)
mp_classif_xgbTree <- model_performance(explainer_classif_xgbTree)
#mp_classif_logicBag <- model_performance(explainer_classif_logicBag)
```

>>>>

# final cleanup and factoring  
aoc_z$Species <- as.factor(paste(aoc_z$genus,aoc_z$species)) #must make value 'Species" (uppercase)
aoc_z$Group <- as.factor(aoc_z$organism.group) #must make value "Group"
aoc_z$Group <- fct_explicit_na(aoc_z$Group) #makes sure that species get counted even if they're missing a group
```
## Data Selection
```{r}
df <- aoc_z %>% 
  filter(tech.tier.zero == "N") %>% #gives studies that pass technical quality criteria
  filter(risk.tier.zero == "N") %>%  #only studies applicable for risk assessment. VERY RESTRICTIVE 
  dplyr::select(c(organism.group, exposure.duration.d, lvl1_f, dose.um3.mL.master, dose.mg.L.master, dose.particles.mL.master, life.stage, bio.org, polymer, shape, size.length.um.used.for.conversions, treatments, effect, effect.metric, particle.volume.um3, density.mg.um.3, environment, exposure.route, lvl2_f)) %>% 
  mutate(effect.metric = as.character(effect.metric)) %>% 
  mutate(effect.metric = (case_when(
    effect.metric == "NONEC" ~ "NOEC",
    effect.metric == "HONEC" ~ "NOEC",
    effect.metric == "LOEC" ~ "LOEC",
    effect.metric == "LC50" ~ "LC50",
    effect.metric == "EC50" ~"EC50",
    effect.metric == "EC10" ~ "EC10"
  ))) %>% 
  mutate(effect.metric = replace_na(effect.metric,"not_available")) %>% 
  mutate(effect.metric = as.factor(effect.metric)) %>% 
  drop_na() %>%  #drop missing
mutate_if(~is.numeric(.) && (.) > 0, log10) %>% 
  mutate(effect_10 = case_when( #convert ordinal to numeric
      effect == "Y" ~ 1,
      effect == "N" ~ 0
    )) %>%
  mutate(effect_10 = factor(effect_10)) %>% 
  dplyr::select(-(effect))

@@

@@

explainer_classif_xgbTree <- DALEX::explain(classif_svm,  label = "eXtreme Gradient Boosting Trees", 
                                        data = test, y = yTest)
```
# Modelling
## Model Performance
```{r model performance, include=FALSE}
mp_classif_rf <- model_performance(explainer_classif_rf)
mp_classif_glm <- model_performance(explainer_classif_glm)
mp_classif_svm <- model_performance(explainer_classif_svm)
mp_classif_decTree <- model_performance(explainer_classif_decTree)
mp_classif_nnet <- model_performance(explainer_classif_nnet)
mp_classif_xgbTree <- model_performance(explainer_classif_xgbTree)
```
